This is the title [Article v\versionnumber]

### 2022-05-19 manuscript/manuscript.tex

Here, we aim to guide the reader through a GIST analysis of the streptavidin-biotin complex. The goal is to
\begin{enumerate}
	\item compute the binding free energy of the complex from the individual energy contributions combined with the contribution of hydration computed using GIST.
	\item visualize local contributions to $\dgsolv$ in the streptavidin binding pocket as well as around biotin.
\end{enumerate}

@@

Compute the atom positions that define the integration region.
For the streptavidin integral, we align the complex structure onto the streptavidin structure and then use the biotin positions as centers.
Note that we use \software{mdtraj} here, since \software{gisttools} stores the reference structure as a \inlinecode{mdtraj.Trajectory} object, but any other library for post-processing of trajectories works as well.
\begin{lstlisting}[style=python]
col = 'dTSsix_dens'
def select(traj, sel):
    "Slice a Trajectory by selection mask."
    return traj.atom_slice(traj.top.select(sel))
# we multiply by 10 to convert nm to Angstrom.
compl_x = select(compl.struct, biotin_mask).xyz[0] * 10.
biotin_x = select(biotin.struct, biotin_mask).xyz[0] * 10.
aligned = compl.struct[:].superpose(strept.struct, \
    atom_indices=strept.struct.top.select(strept_mask))
aligned = select(aligned, biotin_mask)
strept_x = aligned.xyz[0] * 10.

@@

\begin{table}
	\caption{Free energy contributions for the monomers and the dimer.}\label{tab_dg_monomers_dimer}
	\begin{tabular}{lrrrr}
		System       & E(internal) & $\Delta$E(GIST) & $\Delta$S(GIST) & total \\
		complex      & -1303.4 & -361.2 & -233.1 & -226.7 \\
		streptavidin & -1180.7 & -360.8 & -242.4 & -217.1 \\
		biotin       & -24.0   &  -98.1 &  -35.1 & -161.1 \\
		Diff         & -98.7   &   97.7 &   44.4 &  -45.4
	\end{tabular}
\end{table}

@@

In this case, we find that the energy of solvation and the internal energy of the complex more or less cancel out, indicating that binding is largely entropy-driven in this case.
This is somewhat surprising, since isothermal titration calorimetry (ITC) of biotin-streptavidin shows strong enthalpic binding contributions.\cite{mpye2020-biotin-itc}\cite{hyre2006-biotin-itc}
%\section{Content and links}
%
%A tutorial will normally draw on additional files and materials; clearly indicate where and how these are available, with links, and how they are being archived for the long-term and maintained so they stay current.
%You will likely want to reference your GitHub repository as a central point to access all of this information, and then the GitHub repository may link out to other content as needed.

>>>>

\section{Tutorial}
Here, we aim to guide the reader through a GIST analysis of the streptavidin-biotin complex. The goal is to
\begin{enumerate}
	\item compute the binding free energy of the complex from the individual energy contributions combined with the contribution of hydration computed using GIST.
	\item visualize local contributions to $\dgsolv$ in the streptavidin binding pocket as well as around biotin.
\end{enumerate}

@@

Compute the atom positions that define the integration region.
For the streptavidin integral, we align the complex structure onto streptavidin and then use the biotin positions as centers.
Note that we use \software{mdtraj} here, since \software{gisttools} stores the reference structure as a \inlinecode{mdtraj.Trajectory} object, but any other library for post-processing of trajectories works as well.
\begin{lstlisting}[style=python]
col = 'dTSsix_dens'
def select(traj, sel):
    "Slice a Trajectory by selection mask."
    return traj.atom_slice(traj.top.select(sel))
# we multiply by 10 to convert nm to Angstrom.
compl_x = select(compl.struct, biotin_mask).xyz[0] * 10.
biotin_x = select(biotin.struct, biotin_mask).xyz[0] * 10.
aligned = compl.struct[:].superpose(strept.struct, \
    atom_indices=strept.struct.top.select(strept_mask))
aligned = select(aligned, biotin_mask)
strept_x = aligned.xyz[0] * 10.

@@

\begin{table}
	\caption{Free energy contributions for the monomers and the dimer.}\label{tab_dg_monomers_dimer}
	\small
	\begin{tabular}{lrrrrr}
		\toprule
		System       & E(internal) & $\Delta E^\textit{GIST}$ & $\Delta S^\textit{GIST}$ & $\Delta S^\textit{scaled}$ & total \\
		\midrule
		complex      & -1303.4 & -361.2 & -233.1 & -139.9 & -192.0 \\
		streptavidin & -1180.7 & -360.8 & -242.4 & -145.4 & -188.4 \\
		biotin       & -24.0   &  -98.1 &  -35.1 &  -21.1 & -105.4 \\
		Diff         & -98.7   &   97.7 &   44.4 &   26.6 &  -27.6
	\end{tabular}
\end{table}

@@

In this case, we find that the energy of solvation and the internal energy of the complex more or less cancel out, indicating that binding is largely entropy-driven in this case.
This is somewhat surprising, since isothermal titration calorimetry (ITC) of biotin-streptavidin shows strong enthalpic binding contributions.\cite{mpye2020-biotin-itc}\cite{hyre2006-biotin-itc}

\subsection{Further steps}
%\section{Content and links}
%
%A tutorial will normally draw on additional files and materials; clearly indicate where and how these are available, with links, and how they are being archived for the long-term and maintained so they stay current.
%You will likely want to reference your GitHub repository as a central point to access all of this information, and then the GitHub repository may link out to other content as needed.
